Multi-view 3D Aerosol Distribution Recovery

### 2013-07-28 article.tex
bookmark

\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MC simulation (\cref{sec:monte-carlo-simul}).  [c] Cross
    section along the }
  \label{fig:simulation-results1}
\end{figure}
To test the model, we simulated several atmospheric models. Here are
the details.

@@

\noindent{\bf Dimensions}: The sky domain has area of \SI{50 x
  50}{\km} extending from the ground up to altitude of
\SI{10}{\km}. This volume is divided into a rectilinear grid. We used
different grid sizes from \num{50 x 50 x 100} grid, where each voxel
has area of \SI{1 x 1}{\km} and vertical thickness of \SI{100}{\metre}
and down to \num{10 x 10 x 20} grid, where each voxel has area of
\SI{5 x 5}{\km} and vertical thickness of \SI{500}{\metre}.

@@

We simulated various spatial distributions, as a product of two
functions. The first function is an exponential decay~\cite{Levi1980}
with altitude $h(k)$ of voxel $k$,
\begin{align}
  w_1[h(k)] = \frac{1} {n^{sea level}}
  \exp\left[-\frac{h(k)}{H^\mathrm{aerosol}}\right],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. This expresses a general trend
of reduced atmospheric density with height.

The second function, $w_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  w_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bm n}^{\rm true}={\bm w}_1\odot {\bm w}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:two_clouds_sim}a): the first is centered at altitude
\SI{3.3}{\km}, and has horizontal width of \SI{32}{\km} and vertical
thickness of \SI{2.8}{\km}. The second ellipsoid is centered at
altitude \SI{6.6}{\km}, and has lateral width of \SI{24}{\km} and
vertical thickness of \SI{2.1}{\km}. Note that the horizontal widths
are much larger than the vertical ones. This is consistent with scales
of atmospheric aerosol distributions.

\noindent{\bf Cameras}: Each ground-based camera has a hemispherical
field of view, capturing the entire sky from its viewpoint. We used
different numbers of cameras ranging from 12 viewpoints to 100, on a
grid.  The resolution of each camera is low, expressing the fact that
cloudless (yet hazy) sky images are rather smooth.  For example,
\cref{fig:simulation-results1}b shows an example of a modeled
photograph of the {\em Haze Blobs} scene that corresponds to
\cref{fig:two_clouds_sim}a.

@@

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in \cref{fig:two_clouds_sim}a, while the
recovered 3D distribution is visualized in
\cref{fig:two_clouds_sim}b. The distributions appear consistent,
though there are errors that stem from the random noise in the
images. To quantify the results, we use a relative error measure based
on the $\ell_1$ norm
\begin{equation}
  \label{eq:ndiff}
  \epsilon=\frac{\| \hat{\bm n}  - {\bm n}^{\rm true} \|_1}
  {\| {\bm n}^{\rm true} \|_1} ,
\end{equation}
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
the {\em Haze Blobs} case, $\epsilon=0.202$.

We created a {\em Haze Front} scene. \cref{fig:front_sim}a shows an
iso-surface visualization of this distribution.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/two_clouds}}
  \caption{\small [a] Simulated 3D aerosol distribution composed of
    {\em Haze Blobs} and [b] its reconstruction. Color represents
    aerosol density. The density units are $10^{6}~{\rm
      particles}/{\rm m}^3.$}
  \label{fig:two_clouds_sim}
\end{figure}
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/front}}
  \caption{\small [a] Simulated 3D aerosol distribution composed of a
    {\em Haze Front}. [b] Its reconstruction. Color represents aerosol
    density. The density units are $10^{6}~{\rm particles}/{\rm
      m}^3.$}
  \label{fig:front_sim}
\end{figure}
Here an ellipsoid degenerated to an elliptic cylinder that partly
enters the analyzed volume. It is centered at altitude \SI{5}{\km},
has vertical thickness of \SI{4}{\km} and length of \SI{32}{\km} (only
part of which enters the volume). The haze front stretches across the
width of the volume.  \cref{fig:front_sim}b visualizes the recovered
3D distribution of this scene. For the {\em Haze Front},
$\epsilon=0.198$.

>>>>

\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MC simulation (\cref{sec:monte-carlo-simul}).  [c] Cross
    section along the }
  \label{fig:simulation-results1}
\end{figure}
To test the models, we simulated several atmospheric scenarios. Here
are the details.

@@

\noindent{\bf Dimensions}: The sky domain has area of \SI{50 x
  50}{\km} extending from the ground up to altitude of
\SI{10}{\km}. This volume is divided into a rectilinear grid. We used
different grid sizes from \num{10 x 10 x 20} grid, where each voxel
has area of \SI{5 x 5}{\km} and vertical thickness of \SI{500}{\metre}
and up to \num{50 x 50 x 100} grid, where each voxel has area of \SI{1
  x 1}{\km} and vertical thickness of \SI{100}{\metre}.

@@

We simulated various spatial distributions, as a product of two
functions. The first function is an exponential decay~\cite{Levi1980}
with altitude $h(k)$ of voxel $k$,
\begin{align}
  w_1[h(k)] = \sfrac{1} {n^{sea level}}
  \exp\left[-\sfrac{h(k)}{H^\mathrm{aerosol}}\right],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. This expresses a general trend
of reduced atmospheric density with height.

The second function, $w_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  w_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bm n}^{\rm true}={\bm w}_1\odot {\bm w}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:results}a): the first is centered at altitude
\SI{3.3}{\km}, and has horizontal width of \SI{32}{\km} and vertical
thickness of \SI{2.8}{\km}. The second ellipsoid is centered at
altitude \SI{6.6}{\km}, and has lateral width of \SI{24}{\km} and
vertical thickness of \SI{2.1}{\km}. Note that the horizontal widths
are much larger than the vertical ones. This is consistent with scales
of atmospheric aerosol distributions.

\noindent{\bf Cameras}: Each ground-based camera has a hemispherical
field of view, capturing the entire sky from its viewpoint. We used
different numbers of cameras ranging from 12 viewpoints to 100, on a
grid.  The resolution of each camera is low, expressing the fact that
cloudless (yet hazy) sky images are rather smooth.  For example,
\cref{fig:simulation-results1}a and \cref{fig:simulation-results1}b
show example photographs of the {\em Haze Blobs} scene as simulated by
the Single Scattering model and MC model, respectively, from the same
viewing point.  \cref{fig:simulation-results1}c compares a cross section
of the photographs along the horizontal Axis.

@@

An iso-surface visualization of the original {\em Haze Blobs}
distribution is shown in \cref{fig:results}a. \cref{fig:results}c show
the reconstructed scene based on images simulated by the Single
Scattering model. \cref{fig:results}e visualizes the reconstructed
scene based on images simulated by the MC model. The distributions
appear consistent, though there are errors that stem from the random
noise in the images. To quantify the results, we use a relative error
measure based on the $\ell_1$ norm
\begin{equation}
  \label{eq:ndiff}
  \epsilon=\frac{\| \hat{\bm n}  - {\bm n}^{\rm true} \|_1}
  {\| {\bm n}^{\rm true} \|_1} ,
\end{equation}
It is equivalent to the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene.  In
the {\em Haze Blobs} case, $\epsilon=0.571$ and $\epsilon=0.72$ for
the reconstructions based on the Single-Scattering images and MC
images respectively.

We created a {\em Haze Front} scene. \cref{fig:results}b shows an
iso-surface visualization of this distribution.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
  \caption{\small [a] and [b] Simulated 3D aerosol distribution
    composed of a {\em Haze Front} and {\em Haze Front}
    respectively. [c] and [d] Reconstruction of the same scenes when
    using Single-Scattering simulated images as input.  [e] and [f]
    Reconstruction of the scenes when using MC simulated images as
    input.  Color represents aerosol density. The density units are
    $10^{6}~{\rm particles}/{\rm m}^3.$}
  \label{fig:results}
\end{figure}
Here an ellipsoid degenerated to an elliptic cylinder that partly
enters the analyzed volume. It is centered at altitude \SI{5}{\km},
has vertical thickness of \SI{4}{\km} and length of \SI{32}{\km} (only
part of which enters the volume). The haze front stretches across the
width of the volume.  \cref{fig:results}d and \cref{fig:results}f
visualizes the recovered 3D distribution of this scene. For the {\em
  Haze Front}, $\epsilon=0.46$ and $\epsilon=0.62$ for the
reconstructions based on the Single-Scattering images and MC images
respectively.
